Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-06-26 content/contribution/R4.tex

\begin{nestedsection}{R4: Rule-based Reasoning over RDF streams using Rete}{implementation}
	As a proof of concept, we have implemented R4: a Rule-based Reasoner for RDF-streams using Rete.
	Reasoning in R4 is performed continuously and incrementally as dataflow networks that work directly on RDF streams.
	The system architecture is shown in \reffig{R4-architecture}.
	\begin{figure}[t]
		\centering
		\includegraphics[width=0.45\textwidth]{R4-architecture}
		\caption{The system architecture of R4.}
		\labelfig{R4-architecture}
	\end{figure}

	A rule document containing any number of rules is submitted to the system.
	We have chosen RIF-Core to be the language in which rules can be represented, for being compatible with RDF and other semantic web standards.
	The rule document specifies any domain-specific rules as well as an entailment regime \emph{if any} for background reasoning.
	We also added a simple extension to RIF-Core to enable users to specify window constraints as part of their rules, as shown in Listing~\ref{lst-S-RIF-Core}.
	\begin{figure*}
		\centering
		\begin{lstlisting}[caption=Streaming RIF-Core Grammar,label=lst-S-RIF-Core]
Document       ::= IRIMETA? 'Document' '(' Base? Prefix* Import* Group?')'
Base           ::= 'Base' '(' ANGLEBRACKIRI ')'
Prefix         ::= 'Prefix' '(' Name ANGLEBRACKIRI ')'
Import         ::= IRIMETA? 'Import' '(' LOCATOR PROFILE? ')'
Group          ::= IRIMETA? 'Group' '(' (RULE | Group)*')' 
RULE           ::= ((IRIMETA? 'Forall' Var+ '(' CLAUSE')') | CLAUSE)
CLAUSE         ::= Implies | ATOMIC
Implies        ::= IRIMETA? (ATOMIC | 'And' '(' ATOMIC* ')') ':-' FORMULA
LOCATOR        ::= ANGLEBRACKIRI
PROFILE        ::= ANGLEBRACKIRI Window?
Window         ::= Number TimeUnit
TimeUnit       ::= 'ms' | 's' | 'm' | 'h'
		\end{lstlisting}
	\end{figure*}

>>>>

\include{ebnf}
\begin{nestedsection}{R4: Rule-based Reasoning over RDF streams using Rete}{implementation}
	As a proof of concept, we have implemented R4: a Rule-based Reasoner for RDF-streams using Rete.
	Reasoning in R4 is performed continuously and incrementally as dataflow networks that work directly on RDF streams.
	The system architecture is shown in \reffig{R4-architecture}.
	\begin{figure}[t]
		\centering
		\includegraphics[width=0.45\textwidth]{R4-architecture}
		\caption{The system architecture of R4.}
		\labelfig{R4-architecture}
	\end{figure}

	A rule document containing any number of rules is submitted to the system.
	We have chosen RIF-Core to be the language in which rules can be represented, for being compatible with RDF and other semantic web standards.
	The rule document specifies any domain-specific rules as well as an entailment regime \emph{if any} for background reasoning.
	We also added a simple extension to RIF-Core to enable users to specify window constraints as part of their rules, as shown in Listing~\ref{lst-S-RIF-Core}.

\begin{figure*}
\begin{ebnf}
\Rule{Document}{
        \Optional{\NTerm{IRIMETA}} 
        \Token{Document} 
        \Token{(} 
        \Optional{\NTerm{Base}} 
        \ZeroOrMore{\NTerm{Prefix}} 
        \ZeroOrMore{\NTerm{Import}} 
        \Optional{\NTerm{Group}} 
        \Token{)}
}
\Rule{Base}{
        \Token{Base} 
        \Token{(} 
        \NTerm{ANGLEBRACKIRI} 
        \Token{)}
}
\Rule{Prefix}{
        \Token{Prefix} 
        \Token{(} 
        \NTerm{Name} 
        \NTerm{ANGLEBRACKIRI} \Token{)}
}
\Rule{Import}{
        \Optional{\NTerm{IRIMETA}} 
        \Token{Import} 
        \Token{(} 
        \NTerm{LOCATOR} 
        \Optional{\NTerm{PROFILE}} 
        \Token{)}
}
\Rule{Group}{
        \Optional{\NTerm{IRIMETA}} 
        \Token{Group} 
        \Token{(} 
        \ZeroOrMore{\OrList{\NTerm{RULE} \OrSep \NTerm{Group}}} 
        \Token{)}
}
\Rule{RULE}{
        \Optional{\NTerm{IRIMETA}}
        \Token{Forall}
        \OneOrMore{\NTerm{Variable}}
        \Token{(}
        \NTerm{CLAUSE}
        \Token{)}
}
\OrRule{
        \NTerm{CLAUSE}
}
\Rule{CLAUSE}{
        \OrList{\NTerm{Implies} \OrSep \NTerm{ATOMIC}}
}
\Rule{Implies}{
        \Optional{\NTerm{IRIMETA}}
        \OrList{\NTerm{ATOMIC} \OrSep \Token{And} \Token{(} \ZeroOrMore{ATOMIC} \Token{)}}
        \Token{:-}
        \NTerm{FORMULA}
}
\Rule{LOCATOR}{
        \NTerm{ANGLEBRACKURI}
}
\Rule{PROFILE}{
        \NTerm{ANGLEBRACKURI} 
        \Optional{\NTerm{Window}}
}
\Rule{Window}{
        \NTerm{Number}
        \NTerm{TimeUnit}
}
\Rule{TimeUnit}{
        \OrList{\Token{ms} \OrSep \Token{s} \OrSep \Token{m} \OrSep \Token{h}}
}
\end{ebnf}
\caption{Streaming RIF-Core Grammar}
\label{lst-S-RIF-Core}
\end{figure*}
